Papers

### 2024-10-05 quarto/index.qmd
update

@@

* Join us for a 2025 research internship! I'm hiring early this year so just email me.
* <a href="https://ai.meta.com/blog/meta-llama-3-1/" target="_blank">Llama 3.1 405B</a> is now openly available. <a href="https://x.com/astonzhangAZ/status/1815763885380747422" title="Tweet" target="_blank"><img src="./img/logo-twitter.svg" class="paper-icon"></a>
* Meet <a href="https://ai.meta.com/blog/meta-llama-3/" target="_blank">Llama 3</a>, our state-of-the-art open source large language model. Check out <a href="https://x.com/AIatMeta/status/1806757387677897206" target="_blank">my developer podcast</a>. <a href="https://x.com/astonzhangAZ/status/1780990210576441844" title="Tweet" target="_blank"><img src="./img/logo-twitter.svg" class="paper-icon"></a>

@@

>>>>

Current research interests: pre-training architectures & scaling, long context (Llama 4).

@@

* Join us for a 2025 research internship! Just email me if you are interested in improving Llama with our team.
* <a href="https://ai.meta.com/blog/meta-llama-3-1/" target="_blank">Llama 3.1 405B</a> is now openly available. <a href="https://x.com/astonzhangAZ/status/1815763885380747422" title="Tweet" target="_blank"><img src="./img/logo-twitter.svg" class="paper-icon"></a>
* Meet <a href="https://ai.meta.com/blog/meta-llama-3/" target="_blank">Llama 3</a>, our state-of-the-art open source large language model. Check out <a href="https://x.com/AIatMeta/status/1806757387677897206" target="_blank">my developer podcast</a>. <a href="https://x.com/astonzhangAZ/status/1780990210576441844" title="Tweet" target="_blank"><img src="./img/logo-twitter.svg" class="paper-icon"></a>

@@

* M. Zhong\*, **A. Zhang**\*, X. Wang, R. Hou, W. Xiong, C. Zhu, Z. Chen, L. Tan, C. Bi, M. Lewis, S. Popuri, S. Narang, M. Kambadur, D. Mahajan, S. Edunov, J. Han, and L. van der Maaten (\*equal contribution)<br>
<a href="https://arxiv.org/abs/2409.19951" target="_blank">Law of the Weakest Link: Cross Capabilities of Large Language Models</a><br>
*"Cross-capability performance is limited by the weakest underlying capability."*
In *arXiv*, 2024<br>
<a href="https://x.com/astonzhangAZ/status/1841131443420008918" title="Tweet" target="_blank"><img src="./img/logo-twitter.svg" class="paper-icon"></a>
<a href="https://github.com/facebookresearch/llm-cross-capabilities" title="Code" target="_blank"><img src="./img/logo-github.svg" class="paper-icon"></a>
<a href="https://www.llm-cross-capabilities.org" target="_blank">llm-cross-capabilities.org</a>
